Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-29 paper/main.tex
removes footnote
Co-Authored-By: Vince Knight <vincent.knight@gmail.com>

The distributions of the SSE across the tournament types suggest that successful
strategies exhibit some extortionate behaviour, but not constantly.
ZDs are a set of strategies that are often envious as they try to exploit their
opponents. The winners of the tournaments considered in this work are
envious, but not as much as many ZDs.
Though the exact interactions between the matches have not been recorded here,
the work of~\cite{Harper2017} which introduced the trained strategies that
appeared in the top ranked strategies of Section~\ref{section:top_performances}
did. In~\cite{Harper2017} it was shown that clever strategies managed to achieve
mutual cooperation with stronger strategies whilst exploiting the weaker
strategies. This could explain the clever winners
of our analysis, and would explain the SSE distributions. This could also
be the reason why ZDs fail to appear in the tops ranks -- they try to exploit
all opponents and cannot actively adapt back to mutual cooperation against
stronger strategies, which requires more depth of memory. \footnote{Note that
ZDs also tend to perform poorly in population games for a similar reason: they
attempt to exploit other players using ZDs, failing to form a cooperative
subpopulation. This makes them good invaders but poor resisters of invasion.}

>>>>

The distributions of the SSE across the tournament types suggest that successful
strategies exhibit some extortionate behaviour, but not constantly.
ZDs are a set of strategies that are often envious as they try to exploit their
opponents. The winners of the tournaments considered in this work are
envious, but not as much as many ZDs.
Though the exact interactions between the matches have not been recorded here,
the work of~\cite{Harper2017} which introduced the trained strategies that
appeared in the top ranked strategies of Section~\ref{section:top_performances}
did. In~\cite{Harper2017} it was shown that clever strategies managed to achieve
mutual cooperation with stronger strategies whilst exploiting the weaker
strategies. This could explain the clever winners
of our analysis, and would explain the SSE distributions. This could also
be the reason why ZDs fail to appear in the tops ranks -- they try to exploit
all opponents and cannot actively adapt back to mutual cooperation against
stronger strategies, which requires more depth of memory. Note that
ZDs also tend to perform poorly in population games for a similar reason: they
attempt to exploit other players using ZDs, failing to form a cooperative
subpopulation. This makes them good invaders but poor resisters of invasion.
